Effects of Different Pain Relievers and Dosages on Cognitive Retention

### 2025-03-11 paper/paper.qmd
box plots updated

```{r}
#| label: tbl-summary-1
#| tbl-cap: "Summary Statistics for Quantitative Variables"
#| echo: false
#| warning: false
#| message: false
library(knitr)
library(stringr)

@@

```{r}
library(dplyr)
library(knitr)

@@

# Step 4: Display the table
kable(improvement_summary, caption = "Mean Improvement in Game Scores by Drug", booktabs = TRUE, row.names = FALSE)

@@

>>>>

```{r}
#| label: tbl-summary-1
#| tbl-cap: "Summary Statistics for Quantitative Variables"
#| echo: false
#| warning: false
#| message: false
library(knitr)
library(dplyr)
library(stringr)

@@

```{r}

#| label: tbl-summary-1
#| tbl-cap: "Mean Improvement in Game Scores by Drug"
#| echo: false
#| warning: false
#| message: false

@@

# Step 4: Display the table
kable(improvement_summary, booktabs = TRUE, row.names = FALSE)

@@

```{r}

#| label: fig-boxplot-scores
#| echo: false
#| warning: false
#| message: false
#| fig.width: 9
#| fig.height: 8
#| dpi: 300
#| fig-cap: "Boxplot of Memory Game Scores Before and After Treatment by Drug Type"

ggplot(clean_data, aes(x = Drug, y = GameScore, fill = Time)) +
  geom_boxplot(position = position_dodge(width = 0.8)) +
  labs(
    title = "Memory Game Scores by Drug Type and Time",
    x = "Drug Type",
    y = "Memory Game Score",
    fill = "Time"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16),
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 12),
    legend.title = element_text(size = 12)
  )
```

```{r}
#| label: fig-boxplot-cards
#| echo: false
#| warning: false
#| message: false
#| fig.width: 9
#| fig.height: 8
#| dpi: 300
#| fig-cap: "Boxplot of Memory Card Scores Before and After Treatment by Drug Type"

ggplot(clean_data, aes(x = Drug, y = CardScore, fill = Time)) +
  geom_boxplot(position = position_dodge(width = 0.8)) +
  labs(
    title = "Memory Card Scores Before and After Treatment by Drug Type",
    x = "Drug Type",
    y = "Memory Card Score",
    fill = "Time"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16),
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 12),
    legend.title = element_text(size = 12)
  )
